Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
write summary / conclusions

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
We then created several general linear model (GLM) contrast to analyze the
corresponding publicly available fMRI datasets of each naturalistic stimulus
\citep{hanke2016simultaneous, hanke2014audiomovie}
(\href{http://www.studyforrest.org}{studyforrest.org}).

@@

% RSC + LOC
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides
and to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

\section{conclusion}

\todo[inline]{scientific data has no conclusion -> last paragraph}

% natural stimulation
Natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, (continuous,)
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental designs.

\begin{itemize}
\item We reuse public data for independent research question
\item GLM based on annotations to operationalize ``spatial perception''
\item Our results add evidence that model-driven analyses based in annotations
can be run on data from naturalistic stimuli to ``localize'' brain activity
correlating with specific perceptual processes.
\item ``localization performance'' relies on how well the model captures
different aspects of the stimuli's feature space.
\item PPA is functionally heterogeneous region
\item a complex but naturally engaging auditory stimulus like an
audiobook might in principle be used as a non-visual localizer for a variety of
brain functions in subjects who are not willing or able to follow task
instructions during brain scanning [would state that explicitly in the summary
at the end].
\end{itemize}

this study shows that already existing, publicly
available data can be re-used for independent research questions that provide
further evidence for existing theories/hypotheses and advance the field by
generating new findings \& hypothesis.

@@

\todo[inline]{everything correct?}
\todo[inline]{Grant or contribution numbers may be acknowledged}
%
COH designed and performed the analyses, and wrote the manuscript.
%
MH provided critical feedback on the procedure and edited the manuscript.
%
SE provided critical feedback.
%
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
annotation of nouns and created its preliminary version.%

@@

\todo{Figures \& Tables have their own section, the editor puts them where he
wants them?}

@@

>>>>

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed under
more ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
We then created several general linear model (GLM) contrasts to analyze the
corresponding publicly available fMRI datasets of each naturalistic stimulus
\citep{hanke2016simultaneous, hanke2014audiomovie}
(\href{http://www.studyforrest.org}{studyforrest.org}).

@@

% RSC + LOC
Apart from the PPA, results revealed significantly increased activity in the
dorsal precuneus and posterior cingulate region (e.g. retrosplenial complex;
RSC) and lateral occipital cortex (LOC; more lateral in the AV stimulus, more
medial in the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides and
to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

\todo[inline]{scientific data has no conclusion -> last paragraph}
\todo[inline]{(2nd part of) following paragraph pretty similar to discussion's
first paragraph}
% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that [might] work together during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
subjects who are not [willing or] able to follow task instructions during brain
scanning.

@@

\todo[inline]{everything correct? Grant or contribution numbers may be acknowledged}
%
COH designed and performed the analyses, and wrote the manuscript.
%
MH provided critical feedback on the procedure and edited the manuscript.
%
SE provided critical feedback.
%
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
annotation of nouns and created its preliminary version.%

@@

\todo[inline]{Figures \& Tables have their own section, the editor puts them
where he wants them?}

@@

% cut anno
\citep{haeusler2016cutanno}
% speech anno
\citep{hausler2021studyforrest}
% audio-description
\citep{hanke2014audiomovie}
% movie
\citep{hanke2016simultaneous}
% localizer
\citep{sengupta2016extension}
